Affective Uplift During Video Game Play: A Naturalistic Case Study

### 2024-04-04 ms.Rmd
Data path in env

library(scales)
library(cmdstanr)
library(splines)
library(emmeans)
library(posterior)
library(lme4)
library(brms)
library(gt)
library(ggstance)
library(ggdist)
library(patchwork)
library(tidyverse)
source("R/functions.R")
source("R/common.R")

@@

# Document options
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.width = 8,
  fig.asp = 0.618
)
```

@@

# Download, unzip data from OSF PWS database
path <- "data-raw/data.zip"
if (!file.exists(path)) {
  dir.create("data-raw", FALSE)
  download.file(
    url = "https://osf.io/download/j48qf/",
    destfile = "data-raw/data.zip"
  )
  dir.create("data", FALSE)
  unzip(
    zipfile = path,
    files = c(
      "data/demographics.csv",
      "data/study_prompt_answered.csv"
    )
  )
}

>>>>

library(papaja)
library(scales)
library(cmdstanr)
library(splines)
library(emmeans)
library(posterior)
library(lme4)
library(brms)
library(ggdist)
library(patchwork)
library(tidyverse)
source("R/functions.R")
source("R/common.R")

@@

# Document options
knitr::opts_chunk$set(
  cache = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 8,
  fig.asp = 0.618
)
```

@@

# Download, unzip data from OSF PWS database
PWS_DATA_PATH <- Sys.getenv("PWS_DATA_PATH", unset = "data-raw/data.zip")
if (!file.exists(PWS_DATA_PATH)) {
  dir.create(
    dirname(PWS_DATA_PATH), 
    showWarnings = FALSE, 
    recursive = TRUE
  )
  download.file(
    url = "https://osf.io/download/j48qf/",
    destfile = PWS_DATA_PATH
  )
  dir.create("data", FALSE)
  unzip(
    zipfile = PWS_DATA_PATH,
    files = c(
      "data/demographics.csv",
      "data/study_prompt_answered.csv"
    )
  )
}
